### 2017-04-11 notes/subnotes/gwas.tex
tmp commit

This chapter will be written using the information from the \citet{Hirschhorn2005} and \citet{McCarthy2008} reviews as a starting point/guide.

@@

In this approach, a set of genes will be chosen based on the biological hypotheses, or the location of the genes that are within previously determined region of linkage.
These studies are made more efficient by the use of \gls{ld}, as less markers will be required to assess multiple variants or genomic regions.
Candidate gene association studies have identified many of the genes that are known to contribute to susceptability to common disease.
With that said, these studies can only identify  a fraction of genetic risk factors, even for diseases with well-known pathophysiology.
Furthermore, it is clear that if the physiological mechanism of a disease is unknown, this approach would not be able to fully explain the genetic basis of the disease.

>>>>

This chapter will be written using the information from the \citet{Hirschhorn2005} and \citet{McCarthy2008} reviews as a starting point/guide.
See \citet{Astle2009} for detailed discussion about relatedness.

@@

In this approach, a set of genes will be chosen based on the biological hypotheses, or the location of the genes that are within previously determined region of linkage.
These studies are made more efficient by the use of \gls{ld}, as less markers will be required to assess multiple variants or genomic regions.
Candidate gene association studies have identified many of the genes that are known to contribute to susceptibility to common disease.
With that said, these studies can only identify  a fraction of genetic risk factors, even for diseases with well-known pathophysiology.
Furthermore, it is clear that if the physiological mechanism of a disease is unknown, this approach would not be able to fully explain the genetic basis of the disease.
